\section{Sample preparation}
\label{sec:Sampleprep}

Sample preparation is a crucial step in conducting experiments. Therefore, this section explains the sample preparation.

\section*{Procedure}

The preparation of solutions is carried out in the chemistry laboratory. The following solutions were prepared:

\begin{enumerate}
\item[(A)] ZnTPP in benzonitrile, 0.8 mM (approximately 10 mL)
\item[(B)] ZnTPP in toluene, 0.8 mM (approximately 2 mL)
\item[(C)] C70 in benzonitrile, 0.8 mM (approximately 4 mL)
\end{enumerate}

For Solution (A), we measure approximately 10 mL -- the exact number can be taken from the
lab report attached in the appendix~\ref{appA} -- of benzonitrile and transfer it to a sample vessel with a volume more than 10 mL.
We added ZnTPP to achieve a concentration of 0.8 mM. Through thorough mixing until the ZnTPP is completely
dissolved in the solution.
For solution (B) and (C) we repeated the same with different materials.
The solutions prepared in benzonitrile (solutions A and C) were treated in an ultrasonic bath for twenty minutes.


\subsection*{Transient absorption spectroscopy sample preparation}

The samples for transient absorption spectroscopy listed in list \cref{tab:sample} were prepared as following:



\begin{table}[ht]
    \centering
    \begin{tabular}{c|c}
        \toprule
        Sample number & Description \\
        \midrule
        1 & ZnTPP in benzonitrile, 0.8 mM \\
        2 & ZnTPP in benzonitrile, 0.6 mM \\
        3 & ZnTPP in benzonitrile, 0.4 mM \\
        4 & ZnTPP in benzonitrile, 0.2 mM \\
        5 & ZnTPP : C70 in benzonitrile, 1:0.1 \\
        6 & ZnTPP : C70 in benzonitrile, 1:0.2 \\
        7 & ZnTPP : C70 in benzonitrile, 1:0.3 \\
        8 & ZnTPP in toluene, 0.8 mM \\
        12 & ZnOEP in benzonitrile, 0.8 mM \\
        13 & ZnTPP in benzonitrile, 0.016 mM \\
        14 & ZnTPP in toluene, 0.016 mM \\
        15 & ZnOEP in benzonitrile, 0.08 mM \\
        \bottomrule
    \end{tabular}
    \caption{Samples to be prepared}
    \label{tab:sample}
\end{table}

\subsection*{UV-VIS Sample Preparation}

The samples for UV/VIS absorption spectroscopy are prepared as before, but after preparing the solutions, they are 
transferred into 1 mm quartz cuvettes with a filling volume of approximately 400 $\mu$L and sealed properly.


